---
title: "DM001-2.3"
author: "Becky Mak"
date: "Monday, February 16, 2015"
output: html_document
---
##001. Pattern Discovery in Data Mining
###Week1

###Lecture 2.3: Pattern Discovery Basic Concepts: Compressed Representation: Closed Patterns and Max-Patterns

Preparing the data
```{r results='hide'}
library(arules)
## Input the data
data = list(
  c(1:50),
  c(1:100)
)
## Transform data to `transactions` class
data = as(data, "transactions")

```


Example: Find closed pattern itemsets


>Closed patterns: [*Definition from slide (p.3)*]

>A pattern (itemset) X is closed if X is frequent, and there exists 
>no super-pattern Y כ X, with the same support as X 
```

```{r results='hide'}
## find all closed frequent itemsets
closed <- apriori(data, parameter = list(target = "closed", minlen = 1))
```
```{r}
## Show the result
inspect(closed)
```

Example: Find maximal pattern itemsets

>Max-Patterns: [*Definition from slide (p.4)*]

>A pattern X is a max-pattern if X is frequent
>and there exists no frequent super-pattern Y כ X 

```{r results='hide'}
maximal <- apriori(data, parameter = list(target = "maximally frequent itemsets", minlen = 1))

```

```{r}
inspect(maximal)
```
