---
title: "DM001-4"
author: "Becky Mak"
date: "Wednesday, February 18, 2015"
output: html_document
---
##001. Pattern Discovery in Data Mining
###Week2

###Lecture 4.1: Pattern Evaluation: Limitation of the Support-Confidence Framework
> Support and Confidence alone may not fully describe the interestingness of the association rule.

Example: 

|Play basketball|Not play basketball|sum(row)
---|---|---|---
Eat cereal|400|350|750
Not eat cereal|200|50|250
sum(col)|600|400|1000

Association rule:

```{r results='hide'}
library(arules)

## Input the data
data = c(
    rep(list(c("B", "C")), 400), 
    rep(list(c("B^c", "C")), 350),
    rep(list(c("B", "C^c")), 200),
    rep(list(c("B^c", "C^c")), 50)
)

## Transform data to `transactions` class
data = as(data, "transactions")

## Find association rules
rules = apriori(data, parameter=list(support = 0.1, 
                                      confidence = 0.1, 
                                      minlen = 2)) 
                                      
inspect(rules)
inspect(rules[c(5,3)])
```

1. play basketball => eat-cereal [400/1000 = 0.4, 400/600 = 0.67]
2. play basketball^c^ => eat-cereal [350/1000 = 0.35, 50/400 = 0.88]

Implies a misleading association rule.

-----

### Lecture 4.2. Pattern Evaluation: Interestingness Measures: Lift and χ2
> Lift: $lift(x, y) = confidence (x, y) / support(x, y) = s(x U y)/ s(x) X s(y)$ 
> Measured the correlation of a single cell in contingency table (/2-way table)

> Result interpretation: 
> * =1: indepedent
> * >1: positive correlated
> * <1: negative correlated

Following the example in lecture 4.1:

```{r}
inspect(rules[c(5,2)])
```

1. lift(B, C) = 400/1000 / (600/1000 X 750/1000) = 0.89
2. lift(B, C^c^) = 200/1000 / (600/1000 X 250/1000) = 1.33

> Chi-square: $\chi^2 = \sum ((observed-expected)^2/ expected)$
> $expected = \sum(row)*\sum(col)/ \sum(total)$
> Measured the correlation of the whole table

> Result interpretation: 
> * =0: indepedent
> * >0 and obs>exp: positive correlated
> * >0 and obs<exp: negative correlated

```{r}
chiSq = interestMeasure(rules[1],  "chiSquare", transactions = data)
chiSq

## Another method using formula calculation:
obs = c(400, 350, 200, 50)
exp = c(750*600, 750*400, 250*600, 250*400)/sum(obs)

sum((obs-exp)^2/exp)
```

Following the example in lecture 4.1:
$\chi^2 = (400-450)^2/450 +...+ (50-100)^2/100 = `r chiSq`$
